Constrained Optimization-Based Neuro-Adaptive Control (CoNAC) for Uncertain Euler-Lagrange Systems Under Weight and Input Constraints

### 2025-04-11 manuscript.tex
new figures
update new simuilation results

\begin{figure*}[!t]
    \centering
    \includegraphics[width=0.9\linewidth]{src/figures/Controller.drawio.png}
    % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CoNAC).}
    \label{fig:ctrl:diagram}
\end{figure*}

@@

First, let us define the filtered tracking error $\fe\in\R^n$ as 
\begin{equation}
    \fe := \dot{\mv e}-\mm\Lambda \mv e
    ,
    \label{eq:err:filtered}
\end{equation}
where $\mv e := \q - \qd$ denotes the tracking error, $\dot{\mv e} := \dq - \dqd$ represents the derivative of the tracking error, and $\mm\Lambda\in\R^{n\times n}$ is a user-designed positive definite matrix.
Since \eqref{eq:err:filtered} is stable system, it implies that $\mv e$ is bounded if $\fe$ is bounded.

@@

For simplicity, each layer's weights are vectorized as $\wth_i:=\myvec(\wV_i)\in\R^{\Xi_i}$, where $\Xi_i:= (l_i+1)l_{i+1}$ is the number of weights in the $i\textsuperscript{th}$ layer. 
The total weight vector $\wth\in\R^{\Xi}$ is defined by augmenting $\wth_i$ for all $i\in [0,\cdots,k]$ as 
\begin{equation}
    \wth := 
    \begin{bmatrix}
        \wth_k\\
        \wth_{k-1}\\
        \vdots\\
        \wth_0
    \end{bmatrix}
    =
    \begin{bmatrix}
        \myvec(\wV_k)\\
        \myvec(\wV_{k-1})\\
        \vdots\\
        \myvec(\wV_0)
    \end{bmatrix},
\end{equation}
where $\Xi={\sum_{i=0}^{k} \Xi_i}$ represents the total number of weights. The gradient of $ \NN({\q}_n;\wth)$ with respect to $\wth$ is defined as
\begin{equation}
    \pptfrac{\NN}{\wth}=
    \begin{bmatrix}
        \pptfrac{\NN}{\wth_k}&
        \pptfrac{\NN}{\wth_{k-1}}&
    \cdots &
        \pptfrac{\NN}{\wth_0}
    \end{bmatrix}
    \in\R^{n \times \Xi}
    \label{eq. nabla phi}
\end{equation}
where
\begin{equation}
    \pptfrac{\NN}{\wth_i} = 
    \begin{cases}
        (\mm I_{l_{k+1}}\otimes \act_{k}^\top  ), 
        &
        i=k,
        \\
        \wV_k^\top   \act_{k}' (\mm I_{l_{k}}\otimes  \act_{k-1}^\top  ), 
        & 
        i=k-1,
        \\
        &
        \vdots 
        \\
        \wV_k^\top   \act'_{k} \cdots \wV_1^\top  \act_1' (\mm I_{l_1}\otimes {\q}_n^\top  ), 
        &
        i = 0,
    \end{cases}
    \label{eq:NN:grad}
\end{equation}
where $\act_i:= \act_i(\NN_{i-1})$ and $\act_i':= \pptfrac{\act_i}{\NN_{i-1}}$.

@@

The control objective can be represented as follows:
\begin{equation}
    \begin{matrix}
        \min_{\estwth} \ J(\fe;\estwth):= 
        \tfrac{1}{2} \fe^\top \fe
        \\ \\
        \begin{aligned}
        \text{s.t. }&c_{j}(\estwth) 
        \le0, \quad j\in\mathcal{I},
        \end{aligned}
    \end{matrix}
    \label{eq:opt:problem1}
\end{equation}
where $J(\fe;\estwth):= \tfrac{1}{2} \fe^\top \fe$ is the objective function.
Inequality constraints $c_j,\ j\in\mathcal{I}$, are imposed during the weight adaptation process to minimize the objective function, where $\mathcal I$ denotes the set of the imposed inequality constraints. 
Here, $\fe$ is considered a pre-defined data or parameter for this optimization problem. The Lagrangian function is defined as
\begin{equation}
    L(
        \fe,\estwth,[\lambda_j]_{j\in\mathcal I}
    ) 
    := 
    J(\fe;\estwth) 
    + 
    \sum_{j\in\mathcal I}
    \lambda_{j}
    c_{j}(\estwth)
    ,
    \label{eq:lagrangian}
\end{equation}
where $\lambda_j$ denotes the Lagrange multiplier for each constraint.

The adaptation laws for $\estwth$ and $[\lambda]_{j\in\mathcal I}$ are derived to solve the dual problem of \eqref{eq:opt:problem1} (\ie  $\min_{\estwth} \max_{[\lambda]_{j\in\mathcal I}}L(\fe,\estwth,[\lambda]_{j\in\mathcal I})$), as follows:
\begin{subequations}
    \begin{align}
            \ddtt{\estwth}
            &
            =
            -\Gamma \pptfrac{L}{\estwth}
            =
            -\Gamma 
            \left(
                \pptfrac{J}{\estwth}
                +
                \textstyle\sum_{j\in\mathcal{I}}
                \lambda_j 
                \pptfrac{c_j}{\estwth}
            \right),
        \label{eq:adap:th}
            \\
            \ddtt\lambda_j
            & 
            = 
            \beta_j\pptfrac{L}{\lambda_j} 
            = 
            \beta_j c_j ,
            \quad \forall j\in\mathcal I,
        \label{eq:adap:lbd}
            \\
            \lambda_j & = \max(\lambda_j,0) ,
        \label{eq:adap:lbd:max}
    \end{align}
    \label{eq:adaptation law}
\end{subequations}
where $\Gamma=\Gamma^\top:=\mydiag([\gamma_1,\cdots,\gamma_n])\in\R^{n\times n}_{>0}$ denotes the adaptation gain (learning rate) and $\beta_j\in\R_{>0}$ denotes the update rate of the Lagrange multipliers in $\mathcal I$, and the arguments of $L$ and $J$ are suppressed for brevity. 
By selecting $\gamma_i\in\R_{>0},\ \forall i\in[1,\cdots,n]$, one can weight the importance of each component of the gradient of the objective function, allowing for a more tailored adaptation process.
The Lagrange multipliers associated with inequality constraints are non-negative, \ie $\lambda_j\ge 0$, and they become zero when their corresponding constraints are inactive. When a constraint $c_j$ becomes active (\ie violated), the corresponding Lagrange multiplier $\lambda_j$ increases to address the violation. Once the violation is resolved and the constraint is no longer active (\ie $c_j < 0$), the multiplier decreases gradually until it returns to zero. Note that this adaption law is similar to the ALM in \cite{Nocedal:2006aa}, where the adaptation law for Lagrange multipliers is given by $\lambda_j\leftarrow \max(\lambda_j-\tfrac{c_j}{\mu},0)$, with $\mu\in\R_{>0}$ being the penalty parameter.

@@

In \cite{Douratsos:2007aa,Saerens:1991aa}, the authors approximate $\pptfrac{\fe}{\rbu}$ as $
    \pptfrac{\fe}{\rbu}
    \approx
    [
        \mysign(\pptfrac{r_i}{\tau_j})
    ]_{i,j\in[1,\cdots,m]}
$ using the sign of each entry (\ie control direction).
However, this method is not suitable for \eqref{eq:sys1}, since the control directions are unknown, but the sign of the control input is known (\ie $\rbM^{-1}$ is positive definite matrix in the view of Property \ref{prop:M}).
Therefore, we propose to approximate $\pptfrac{\fe}{\rbu}$ as $\pptfrac{\fe}{\rbu}\approx \mm I_n$ and one can conclude \eqref{eq:adap:th} as follows:
\begin{equation}
    \ddtt{\estwth}
    \approx
    -\Gamma 
    \left(
        \pptfrac{\estNN}
        {\estwth}^\top
        \fe
        +
        \textstyle\sum_{j\in\mathcal{I}}
        \lambda_j 
        \pptfrac{c_j}{\estwth}
    \right)
    .
    \label{eq:adap:th:approx}
\end{equation}

%% ALGORITHM PART; Now omitted!
% The proposed controller is implemented using Algorithm \ref{alg: alg1}. For implementation in the discrete-time domain, it is recommended to use a sufficiently small sampling time $T_s$. If a large $T_s$ is used, $\Gamma$ and $\beta_j$ should satisfy the Armijo condition \cite[Chap.~3 eq.~(3.4)]{Nocedal:2006aa} to ensure that the objective function decreases.

@@

To investigate the boundedness of $\estwth_k$, consider the Lyapunov function candidate $V_2:=\tfrac{1}{2}\estwth_k^\top\Gamma^{-1} \estwth_k$.
Taking the time derivative of $V_2$ yields:
\begin{equation}
    \begin{aligned}
        \ddtt  V_2 
        =& 
        -\estwth_k^\top 
        \Gamma^{-1}\Gamma
        (
            (\mm I_{l_{k+1}}\otimes \hat\act_k^\top)^\top
            \fe
            +
            \textstyle\sum_{j\in\mathcal{I}}
            \lambda_j 
            \pptfrac{c_j}{\estwth_k}
        )
        \\
        =&
        -\estwth_k^\top 
        (
            (\mm I_{l_{k+1}}\otimes \hat\act_k^\top)^\top
            \fe
            +
            \lambda_{\theta_k}\estwth_k
        \\
        &
            +
            \textstyle\sum_{
                j\in\mathcal{I}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
            }
            \lambda_j 
            \pptfrac{c_j}{\estwth_k}
        )
        \\
        \le&
        -
        \lambda_{\theta_k}\norm{\estwth_k}^2
        +
        \underbrace{
            \norm{(\mm I_{l_{k+1}}\otimes \hat\act_k^\top)}
        }_{:=c_1\in\R_{>0}}
        \norm{\fe}
        \norm{\estwth_k}
        \\
        &
        -
        \underbrace{
        \textstyle\sum_{
            j\in\mathcal{I}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
        }
        \lambda_j 
        \estwth_k^\top \pptfrac{c_j}{\estwth_k}
        }_{:= c_2 >0,\ \text{by Lemma \ref{lem:convex:angle} and Assumption \ref{assum:LICQ}}}
        \\
        \le&
        -
        \lambda_{\theta_k}\norm{\estwth_k}^2
        +
        c_1     
        \norm{\fe}
        \norm{\estwth_k}
        .
    \end{aligned}
    \label{eq:lya2:dot}
\end{equation}
According to \eqref{eq:lya2:dot}, the invariant set of $\estwth_k$ is defined as
\begin{equation}
    \Theta_{\theta_k}^{c_1} 
    = 
    \left\{ 
        \estwth_k \in \R^{\Xi_{k}} 
        \mid 
        \norm{\estwth_k} 
        \le 
        \tfrac{
            c_1(2\overline\tau+\overline\tau_d)
        }{
            \lambda_{\theta_k}\lambda_{\min}(\mm K)
        }
    \right\}
    .
    \label{eq:invariant:c1:wth}
\end{equation}

@@

The boundedness of inner layers' weights and satisfactions of their constraints $c_j,\ \forall j\in\{\theta_i\}_{i\in[k-1,\cdots,0]}$ can be shown recursively, using \cite[Chap.~4 T.~1.9]{Desoer:2009aa}
The dynamics of $\estwth_i,\ \forall i\in[k-1,\cdots,0]$ are represented as
\begin{equation}
    \ddtt \estwth_i 
    =
    -\Gamma
    \left(
        \pptfrac{\estNN}{\estwth_i}^\top
        \fe
        +
        \lambda_{\theta_i}\estwth_i
        +
        \textstyle\sum_{
            j\in\mathcal{I}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
        }
        \lambda_j
        \pptfrac{c_j}{\estwth_i}
    \right)
    .
\end{equation}
Invoking Lemma \ref{lem:cstr:grad:bound}, $\estwth_i$ is bounded, provided that $\estwth_i,\ \forall i\in[k,\cdots,i+1]$ are bounded, since the system matrix $-\lambda_{\theta_i} \mm I_{\Xi_i}$ is stable and the residual terms are bounded.
Therefore, starting from $(k-1)\textsuperscript{th}$ layer, the boundedness of $\estwth_i$ can be established recursively down to the input layer ($i=0$).

@@

% ------------------------------------
% Control Input Saturation
% ------------------------------------
To demonstrate the effectiveness of the proposed CoNAC to handle the combination of the nonlinear input constraints, the saturation function is defined to satisfy the following domain $\Theta_{\mysat}:=\left\{\Theta_{\mysat, {\rbu}}\cap\Theta_{\mysat, {\tau_1}}\right\}$ as depicted in Fig.~\ref{fig:sat}, where
%
\begin{subequations}
    \begin{align}
        \Theta_{\mysat, {\rbu}}
        :=&
        \left\{
            \rbu
            \mid
            \norm{\rbu} \le \overline\tau
        \right\}
        \label{eq:sat:norm}
        ,
        \\
        \Theta_{\mysat, {\tau_1}}
        :=&
        \left\{
            \tau_1
            \mid
            \vert{\tau_1}\vert \le \overline\tau_1
        \right\}
        ,
        \label{eq:sat:tau1}
    \end{align}
    \label{eq:sat}
\end{subequations}
%
\MSRY{CORRECT HERE}
with $\overline\tau=10$ and $\overline\tau_1=9$ are the saturation limit values for the norm of the control input norm and the first links, respectively. 
These domains \ref{eq:sat:norm} and \ref{eq:sat:tau1} can be physically interpreted as a combination of the voltage source limitation of the actuators and the torque limitation of the first link actuator.

@@

% ------------------------------------
% Controllers
% ------------------------------------
For a comparative study, CoNAC with the auxiliary system presented in \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa} (CoNAC-AUX) was implemented, which only considered the weight norm constraint $c_{\theta_i},\ \forall i\in\{0,\cdots,k\}$ and input bound constraint $c_{\overline\tau_1}$ and $c_{\underline\tau_1}$ introduced in \eqref{eq:cstr:input:bound} and not the nonlinear input norm constraint $c_{\rbu}$ \eqref{eq:cstr:input:norm}.
Besides, the proposed controller, CoNAC, rigorously considered the weight norm constraint, and input bound and norm constraints simultaneously within a constrained optimization framework. 
The properties of the controllers are summarized in Table \ref{table:controller}.

% ------------------------------------
% Aux. system in CoNAC-AUX
% ------------------------------------
The auxiliary system in CoNAC-AUX is defined as $\ddtt{\mv\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\tau_{1},\ \mv{\zeta}\vert_{t=0} = 0$, where $\mv{\zeta}\in\R^n$ denotes the auxiliary state, $\mm{A}_\zeta\in\R_{<0}^{n\times n}$ and $\mm{B}_\zeta\in\R^{n\times n}$, and $\Delta\tau_{1} = 
\tau_{1}-\max(\underline\tau_1,\min(\overline\tau_1,\tau_1))$.
The auxiliary state variables were used in the adaptation law \eqref{eq:adap:th:approx} by substituting $\fe$ with $\fe+\mv{\zeta}$.
Hence, the weights are adapted to reduce not only the tracking error $\fe$ but also the auxiliary state $\mv{\zeta}$.

% ------------------------------------
% Controller Parameters
% ------------------------------------
For all controllers (CoNAC, and CoNAC-AUX), the NN input vector ${\q}_n$ was set as ${\q}_n=[\q^\top,\dq^\top,\fe^\top,1]^\top\in\R^{3n+1}$ with the augmented scalar $1$ included to account for the bias term in the weight matrix. 
The NNs' weights were initialized randomly with uniform distribution in the range of $[-0.1,0.1]$.
Each DNN architecture had two hidden layers with eight nodes (\ie $k=2, l_0=6, l_1=4, l_2=4, l_3=2$), and the adaptation gain was set to $\Gamma=\mydiag([1.5,1.0])$. 
The constraint parameters were $\overline\wth_0=11, \overline\wth_1=12$, and $\overline\wth_2=13$. 
The sampling rate of the controller was set to $250$ Hz, and $1000$ Hz for the simulation.

The quantitative comparison of the tracking performance and the control input constraint violations were evaluated using the $L_2$-norm of them, (\ie $\sqrt{\int_0^T\norm{h},\der t}$, where $h\in\{r_1,r_2,\max(0,c_{\rbu}),\max(0,c_{\overline\tau_1}+c_{\underline\tau_1})$ and $T\in\R_{>0}$ denotes the episode duration time.
Note that $c_{\overline\tau_1}$ and $c_{\underline\tau_1}$ can not be active at the same time, so $\max(0,c_{\overline\tau_1}+c_{\underline\tau_1})$ is used to evaluate the control bound constraint violation.
To investigate the parameter dependencies, the parameters of the controllers $\beta_u,\beta_{\overline\tau},\beta_{\underline\tau}$ \MSRY{CORRECT} were varied within the range of \MSRY{SEE HERE} $[0.5,1.5]$ across 100000 samples.

% ------------------------------------
% Controller Table
% ------------------------------------
\begin{table}[t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Properties of the controllers used in simulation}
    \label{table:controller}
    \centering
    \begin{tabular}{c c c}
    \hline
        & \multicolumn{2}{c}{\bf{Handling Capability}}\\
        & Weight Constraint & Input Constraint\\
    \hline
    \hline
    \multirow{2}{*}{\bf{CoNAC}} & O & O \\
        & (by optimization) &  (by optimization)\\
    \hline
    \multirow{2}{*}{\bf{CoNAC-AUX}} & O & $\triangle$ \\
        & (by optimization) & (by aux. system)\\
    \hline
    \end{tabular}
\end{table}

% ------------------------------------
% Parameter Variation 
% ------------------------------------
\begin{figure}[!t]      
    \centering
    {\includegraphics[width=\figSizeOneCol\linewidth]{
        src/measurement/figures/Fig11.eps
    }}
\caption{Box-and-Whisker plot of $L_2$-norms of the tracking performances and control input constraint violations of CoNAC and CoNAC-AUX across various parameter values.}
    \label{fig:ctrl:result:var}
\end{figure}

>>>>

\begin{figure*}[!t]
    \centering
    \includegraphics[width=0.8\linewidth]{src/figures/Controller.drawio.png}
    % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CoNAC).}
    \label{fig:ctrl:diagram}
\end{figure*}

@@

First, let us define the filtered tracking error $\fe\in\R^n$ as 
\begin{equation}
    \fe := \dot{\mv e}-\mm\Lambda \mv e
    ,
    \label{eq:err:filtered}
\end{equation}
where $\mv e := \q - \qd$ denotes the tracking error, $\dot{\mv e} := \dq - \dqd$ represents the derivative of the tracking error, and $\mm\Lambda\in\R^{n\times n}_{>0}$ is a user-designed filtering matrix.
Since \eqref{eq:err:filtered} is stable system, it implies that $\mv e$ is bounded if $\fe$ is bounded.

@@

For simplicity, each layer's weights are vectorized as $\wth_i:=\myvec(\wV_i)\in\R^{\Xi_i}$, where $\Xi_i:= (l_i+1)l_{i+1}$ is the number of weights in the $i\textsuperscript{th}$ layer. 
The total weight vector $\wth\in\R^{\Xi}$ is defined by augmenting $\wth_i$ for all $i\in [0,\cdots,k]$ as 
\begin{equation}
    \wth := 
    \begin{bmatrix}
        \wth_k\\
        \wth_{k-1}\\
        \vdots\\
        \wth_0
    \end{bmatrix}
    =
    \begin{bmatrix}
        \myvec(\wV_k)\\
        \myvec(\wV_{k-1})\\
        \vdots\\
        \myvec(\wV_0)
    \end{bmatrix},
\end{equation}
where $\Xi={\sum_{i=0}^{k} \Xi_i}$ represents the total number of weights. The gradient of $ \NN({\q}_n;\wth)$ with respect to $\wth$ is defined as
\begin{equation}
    \pptfrac{\NN}{\wth}=
    \begin{bmatrix}
        \pptfrac{\NN}{\wth_k}&
        \pptfrac{\NN}{\wth_{k-1}}&
    \cdots &
        \pptfrac{\NN}{\wth_0}
    \end{bmatrix}
    \in\R^{n \times \Xi}
    \label{eq. nabla phi}
\end{equation}
where
\begin{equation}
    \pptfrac{\NN}{\wth_i} = 
    \begin{cases}
        (
            \mm I_{l_{k+1}}
            \otimes 
            \act_{k}^\top  
        )
        , 
        &
        i=k
        ,
        \\
        \wV_k^\top\act_{k}' 
        (
            \mm I_{l_{k}}
            \otimes  
            \act_{k-1}^\top  
        )
        , 
        & 
        i=k-1
        ,
        \\
        &
        \vdots 
        \\
        \wV_k^\top\act'_{k} 
        \cdots 
        \wV_1^\top\act_1' 
        (
            \mm I_{l_1}
            \otimes 
            {\q}_n^\top  
        )
        , 
        &
        i = 0
        ,
    \end{cases}
    \label{eq:NN:grad}
\end{equation}
and $\act_i:= \act_i(\NN_{i-1})$ and $\act_i':= \pptfrac{\act_i}{\NN_{i-1}}$.

@@

The control objective can be represented as follows:
\begin{equation}
    \begin{matrix}
        \min_{\estwth} \ J(\fe;\estwth):= 
        \tfrac{1}{2} \fe^\top \fe₩
        \\ \\
        \begin{aligned}
        \text{subject to }&c_{j}(\estwth) 
        \le0, \quad j\in\mathcal{I},
        \end{aligned}
    \end{matrix}
    \label{eq:opt:problem1}
\end{equation}
where $J(\fe;\estwth):= \tfrac{1}{2} \fe^\top \fe$ is the objective function.
Inequality constraints $c_j,\ j\in\mathcal{I}$, are imposed during the weight adaptation process to minimize the objective function, where $\mathcal I$ denotes the set of the imposed inequality constraints. 
Here, $\fe$ is considered a pre-defined data or parameter for this optimization problem. The Lagrangian function is defined as
\begin{equation}
    L(
        \fe,\estwth,[\lambda_j]_{j\in\mathcal I}
    ) 
    := 
    J(\fe;\estwth) 
    + 
    \sum_{j\in\mathcal I}
    \lambda_{j}
    c_{j}(\estwth)
    ,
    \label{eq:lagrangian}
\end{equation}
where $\lambda_j$ denotes the Lagrange multiplier for each constraint.

The adaptation laws for $\estwth$ and $[\lambda]_{j\in\mathcal I}$ are derived to solve the dual problem of \eqref{eq:opt:problem1} (\ie  $\min_{\estwth} \max_{[\lambda]_{j\in\mathcal I}}L(\fe,\estwth,[\lambda]_{j\in\mathcal I})$), as follows:
\begin{subequations}
    \begin{align}
            \ddtt{\estwth}
            &
            =
            -\alpha \pptfrac{L}{\estwth}
            =
            -\alpha 
            \left(
                \pptfrac{J}{\estwth}
                +
                \textstyle\sum_{j\in\mathcal{I}}
                \lambda_j 
                \pptfrac{c_j}{\estwth}
            \right),
        \label{eq:adap:th}
            \\
            \ddtt\lambda_j
            & 
            = 
            \beta_j\pptfrac{L}{\lambda_j} 
            = 
            \beta_j c_j ,
            \quad \forall j\in\mathcal I,
        \label{eq:adap:lbd}
            \\
            \lambda_j & = \max(\lambda_j,0) ,
        \label{eq:adap:lbd:max}
    \end{align}
    \label{eq:adaptation law}
\end{subequations}
where $\alpha=\in\R_{>0}$ denotes the adaptation gain (learning rate) and $\beta_j\in\R_{>0}$ denotes the update rate of the Lagrange multipliers in $\mathcal I$, and the arguments of $L$ and $J$ are suppressed for brevity. 
% By selecting $\alpha_i\in\R_{>0},\ \forall i\in[1,\cdots,n]$, one can weight the importance of each component of the gradient of the objective function, allowing for a more tailored adaptation process.
The Lagrange multipliers associated with inequality constraints are non-negative, \ie $\lambda_j\ge 0$, and they become zero when their corresponding constraints are inactive. When a constraint $c_j$ becomes active (\ie violated), the corresponding Lagrange multiplier $\lambda_j$ increases to address the violation. Once the violation is resolved and the constraint is no longer active (\ie $c_j < 0$), the multiplier decreases gradually until it returns to zero. Note that this adaption law is similar to the ALM in \cite{Nocedal:2006aa}, where the adaptation law for Lagrange multipliers is given by $\lambda_j\leftarrow \max(\lambda_j-\tfrac{c_j}{\mu},0)$, with $\mu\in\R_{>0}$ being the penalty parameter.

@@

In \cite{Douratsos:2007aa,Saerens:1991aa}, the authors approximate $\pptfrac{\fe}{\rbu}$ as $
    \pptfrac{\fe}{\rbu}
    \approx
    [
        \mysign(\pptfrac{r_i}{\tau_j})
    ]_{i,j\in[1,\cdots,m]}
$ using the sign of each entry (\ie control direction).
However, this method is not suitable for \eqref{eq:sys1}, since the control directions are unknown, but the sign of the control input is known (\ie $\rbM^{-1}$ is positive definite matrix in the view of Property \ref{prop:M}).
Therefore, we propose to approximate $\pptfrac{\fe}{\rbu}$ as $\pptfrac{\fe}{\rbu}\approx \mm I_n$ and one can conclude \eqref{eq:adap:th} as follows:
\begin{equation}
    \ddtt{\estwth}
    \approx
    -\alpha 
    \left(
        \pptfrac{\estNN}
        {\estwth}^\top
        \fe
        +
        \textstyle\sum_{j\in\mathcal{I}}
        \lambda_j 
        \pptfrac{c_j}{\estwth}
    \right)
    .
    \label{eq:adap:th:approx}
\end{equation}

%% ALGORITHM PART; Now omitted!
% The proposed controller is implemented using Algorithm \ref{alg: alg1}. For implementation in the discrete-time domain, it is recommended to use a sufficiently small sampling time $T_s$. If a large $T_s$ is used, $\alpha$ and $\beta_j$ should satisfy the Armijo condition \cite[Chap.~3 eq.~(3.4)]{Nocedal:2006aa} to ensure that the objective function decreases.

@@

To investigate the boundedness of $\estwth_k$, consider the Lyapunov function candidate $V_2:=\tfrac{1}{2\alpha}\estwth_k^\top \estwth_k$.
Taking the time derivative of $V_2$ yields:
\begin{equation}
    \begin{aligned}
        \ddtt  V_2 
        =& 
        -\estwth_k^\top 
        (
            (\mm I_{l_{k+1}}\otimes \hat\act_k^\top)^\top
            \fe
            +
            \textstyle\sum_{j\in\mathcal{I}}
            \lambda_j 
            \pptfrac{c_j}{\estwth_k}
        )
        \\
        =&
        -\estwth_k^\top 
        (
            (\mm I_{l_{k+1}}\otimes \hat\act_k^\top)^\top
            \fe
            +
            \lambda_{\theta_k}\estwth_k
        \\
        &
            +
            \textstyle\sum_{
                j\in\mathcal{I}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
            }
            \lambda_j 
            \pptfrac{c_j}{\estwth_k}
        )
        \\
        \le&
        -
        \lambda_{\theta_k}\norm{\estwth_k}^2
        +
        \underbrace{
            \norm{(\mm I_{l_{k+1}}\otimes \hat\act_k^\top)}
        }_{:=c_1\in\R_{>0}}
        \norm{\fe}
        \norm{\estwth_k}
        \\
        &
        -
        \underbrace{
        \textstyle\sum_{
            j\in\mathcal{I}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
        }
        \lambda_j 
        \estwth_k^\top \pptfrac{c_j}{\estwth_k}
        }_{:= c_2 >0,\ \text{by Lemma \ref{lem:convex:angle} and Assumption \ref{assum:LICQ}}}
        \\
        \le&
        -
        \lambda_{\theta_k}\norm{\estwth_k}^2
        +
        c_1     
        \norm{\fe}
        \norm{\estwth_k}
        .
    \end{aligned}
    \label{eq:lya2:dot}
\end{equation}
According to \eqref{eq:lya2:dot}, the invariant set of $\estwth_k$ is defined as
\begin{equation}
    \Theta_{\theta_k}^{c_1} 
    = 
    \left\{ 
        \estwth_k \in \R^{\Xi_{k}} 
        \mid 
        \norm{\estwth_k} 
        \le 
        \tfrac{
            c_1(2\overline\tau+\overline\tau_d)
        }{
            \lambda_{\theta_k}\lambda_{\min}(\mm K)
        }
    \right\}
    .
    \label{eq:invariant:c1:wth}
\end{equation}

@@

The boundedness of inner layers' weights and satisfactions of their constraints $c_j,\ \forall j\in\{\theta_i\}_{i\in[k-1,\cdots,0]}$ can be shown recursively, using \cite[Chap.~4 T.~1.9]{Desoer:2009aa}
The dynamics of $\estwth_i,\ \forall i\in[k-1,\cdots,0]$ are represented as
\begin{equation}
    \ddtt \estwth_i 
    =
    -\alpha
    \left(
        \pptfrac{\estNN}{\estwth_i}^\top
        \fe
        +
        \lambda_{\theta_i}\estwth_i
        +
        \textstyle\sum_{
            j\in\mathcal{I}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
        }
        \lambda_j
        \pptfrac{c_j}{\estwth_i}
    \right)
    .
\end{equation}
Invoking Lemma \ref{lem:cstr:grad:bound}, $\estwth_i$ is bounded, provided that $\estwth_i,\ \forall i\in[k,\cdots,i+1]$ are bounded, since the system matrix $-\lambda_{\theta_i} \mm I_{\Xi_i}$ is stable and the residual terms are bounded.
Therefore, starting from $(k-1)\textsuperscript{th}$ layer, the boundedness of $\estwth_i$ can be established recursively down to the input layer ($i=0$).

@@

% ------------------------------------
% Control Input Saturation
% ------------------------------------
To demonstrate the effectiveness of the proposed CoNAC to handle the combination of the convex input constraints, the saturation function is defined to satisfy the following domain $\Theta_{\mysat}:=\left\{\Theta_{\mysat, {\rbu}}\cap\Theta_{\mysat, {\tau_2}}\right\}$ as depicted in Fig.~\ref{fig:sat}, where
%
\begin{subequations}
    \begin{align}
        \Theta_{\mysat, {\rbu}}
        :=&
        \left\{
            \rbu
            \mid
            \norm{\rbu} \le 
            10
            % \overline\tau
        \right\}
        \label{eq:sat:norm}
        ,
        \\
        \Theta_{\mysat, {\tau_2}}
        :=&
        \left\{
            \tau_2
            \mid
            \vert{\tau_2}\vert \le 
            2.5
            % \overline\tau_2
        \right\}
        .
        \label{eq:sat:tau2}
    \end{align}
    \label{eq:sat}
\end{subequations}
%
These domains \ref{eq:sat:norm} and \ref{eq:sat:tau2} can be physically interpreted as a combination of the voltage source limitation of the actuators and the torque limitation of the second link actuator.

@@

% ------------------------------------
% Controllers
% ------------------------------------
For a comparative study, we implemented 3 controllers:

% ------------------------------------
% Controllers: CoNAC 
% ------------------------------------
\subsubsection*{Controller 1: (C$_1$) proposed}

To handle the input saturation, the proposed CoNAC was implemented with the input bound constraint for second link $c_{\overline\tau_2}$ and $c_{\underline\tau_2}$ \eqref{eq:cstr:input:bound} and the nonlinear input norm constraint $c_{\rbu}$ \eqref{eq:cstr:input:norm}, as follows:
\begin{equation}
    \begin{aligned}
        c_{\overline\tau_2}     
        =&
        \tau_2-\overline\tau_2
        \le 0
        ,
        \quad
        c_{\underline\tau_2} 
        =&
        \underline\tau_2-\tau_2
        \le 0
        ,
        \quad
        c_{\rbu}
        =&
        \tfrac{1}{2}
        (
            \norm{\rbu}-\overline\tau
        )^2 
        ,
    \end{aligned}
    \label{eq:sim:cstr:CoNAC}
\end{equation}
where $\overline\tau_2=2.5$ and $\underline\tau_2=-2.5$ are the upper and lower bounds of the second link actuator, respectively, and $\overline\tau=10$ is the maximum allowable norm of the control input.
Hence, (C$_1$) is possible to use full capability of the actuator.
The weight constraints $c_{\theta_i},\ \forall i\in[0,\cdots,k]$ were also considered in the CoNAC.
As described in \eqref{eq:control:est}, the control input is equal to the output of the NN $\rbu$, and the adaptation law is defined in \eqref{eq:adaptation law}.

% ------------------------------------
% Controllers: Aux. system in CoNAC-AUX
% ------------------------------------
\subsubsection*{Controller 2: (C$_2$) CoNAC with auxiliary system}

On the other hand, the existing auxiliary system \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa} was used to compare with the proposed (C$_1$).
The auxiliary system is defined as $\ddtt{\mv\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\tau_{1},\ \mv{\zeta}\vert_{t=0} = 0$, where $\mv{\zeta}\in\R^n$ denotes the auxiliary state, $\mm{A}_\zeta\in\R_{<0}^{n\times n}$ and $\mm{B}_\zeta\in\R^{n\times n}$, and $\Delta\tau_{1} = 
\tau_{1}-\max(\underline\tau_1,\min(\overline\tau_1,\tau_1))$.
Since, the auxiliary system only considers the input bound constraint, $\overline{\tau}_1$ is set to $9.682$ to approximately match the maximum allowable norm of the control input $\overline\tau$, \ie $\overline{\tau}_1^2+\overline{\tau}_2^2=\overline{\tau}^2$.

The auxiliary state variables were used in the adaptation law \eqref{eq:adap:th:approx} by substituting $\fe$ with $\fe+\mv{\zeta}$.
Hence, the weights are adapted to reduce not only the tracking error $\fe$ but also the auxiliary state $\mv{\zeta}$.

% ------------------------------------
% Controllers: CoNAC with small beta
% ------------------------------------
\subsubsection*{Controller 3: (C$_3$) CoNAC with small $\beta_i$}

To investigate the effect of the update rate of Lagrange multipliers, C$_3$ was implemented with small $\beta_i$ values.

% ------------------------------------
% Controller Parameters
% ------------------------------------
For all controllers ((C$_1$), (C$_2$), and (C$_3$)), the NN input vector ${\q}_n$ was set as ${\q}_n=[\q^\top,\dq^\top,\fe^\top,1]^\top\in\R^{3n+1}$ with the augmented scalar $1$ included to account for the bias term in the weight matrix. 
The NNs' weights were initialized randomly with uniform distribution in the range of $[-0.1,0.1]$.
Each NN architecture had two hidden layers with eight nodes (\ie $k=2, l_0=6, l_1=4, l_2=4, l_3=2$), and the adaptation gain was set to $\alpha=1$.
The filtering matrix $\mm{\Lambda}$ was set to $\mm{\Lambda}=\mydiag([5,5])$.
The sampling rate of the controller was $250$ Hz, and $1000$ Hz for the simulation.
To emphasize the control input constraint handling capability, the weight constraint parameters were selected sufficiently large (\ie $\overline\wth_0=11, \overline\wth_1=12$, and $\overline\wth_2=13$), avoiding the violation of the weight constraints.
